Project-I by Group Sao Paulo

### 2015-11-02 report/paper.tex
Update report

\begin{figure}[!h] % !t
\center
\subfigure[$y$ in function of $55^{th}$ dimension of $X$.]{\includegraphics[width=2.2in]{figures/dim6.png} \label{fig:reg_dim6}}
\hfill
\subfigure[$y$ in function of $6^{th}$ dimension of $X$.]{\includegraphics[width=2.2in]{figures/dim55.png} \label{fig:reg_dim55}}
\caption{Graphs of $y$ in function of the input dimensions most correlated with the output.}
\end{figure}

@@

Figure ~\ref{fig:reg_alphaRMSE} shows the train and test RMSE for a step size $\alpha$ varied from $10^{-3}$ to $10^{-0.5}$ with $20$ points in between. The convergence condition was reached when the variation of $\beta$ between two iterations was lower than $1.5 \alpha$. Cross-validation was made using $66 \% $ of the data as train data and the rest as test data. We observe that the bias is higher and the variance globally lower for small values of $\alpha$. The RMSE is optimal for $\alpha \approx 0.2$. With higher $\alpha$ values, gradient descent is not able to converge and the error goes to $\infty$.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/alphaRMSEBox.png}
	\caption{Ridge regression for a $66 \%$ - $33 \%$ split with 3 iterations for each $\lambda$.}
	\label{fig:reg_alphaRMSE}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/lambdaRMSE.png}
	\caption{Ridge regression for a $66 \%$ - $33 \%$ split with 3 iterations for each $\lambda$.}
	\label{fig:reg_lambdaRMSE}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/comparisonReg.png}
	\caption{Boxplots of train and test RMSE for least-squares (LS), least-squares with gradient descent (LS-GD) and ridge regression (Ridge).}
	\label{fig:reg_compareMethods}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\subfigure[Histogram of the $23^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim23.png} \label{fig:class_dim23}}
	\hfill
	\subfigure[Histogram of the $35^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim35.png} \label{fig:class_dim35}}
	\caption{Example of histogram to show the distribution of $X$ dimensions. We can see that each distribution is composed of a peak in blue and of a Gaussian in red, separable given the $20^{th}$ variable.}
\end{figure}

@@

Figure ~\ref{fig:class_penLogistic} shows the train and test loss function for $\lambda$ varied from $10^{-3}$ to $1$.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/comparisonReg.png}
	\caption{Boxplots of train and test loss function for penalised logistic regression in function of $\lambda$.}
	\label{fig:class_penLogistic}
\end{figure}

@@

\subsubsection*{References}

>>>>

\begin{figure}[!h] % !t
\center
\subfigure[$y$ in function of $55^{th}$ dimension of $X$.]{\includegraphics[width=2in]{figures/dim6.png} \label{fig:reg_dim6}}
\hfill
\subfigure[$y$ in function of $6^{th}$ dimension of $X$.]{\includegraphics[width=2in]{figures/dim55.png} \label{fig:reg_dim55}}
\caption{Graphs of $y$ in function of the input dimensions most correlated with the output.}
\end{figure}

@@

Figure ~\ref{fig:reg_alphaRMSE} shows the train and test RMSE for a step size $\alpha$ varied from $10^{-3}$ to $10^{-0.5}$ with $20$ points in between. The convergence condition was reached when the variation of $\beta$ between two iterations was lower than $1.5 \alpha$. Cross-validation was made using $66 \% $ of the data as train data and the rest as test data. Train and test RMSE is optimal for $\alpha \approx 0.2$. With higher $\alpha$ values, gradient descent is not able to converge and the error goes to $\infty$.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.6in]{figures/alphaRMSE.png}
	\caption{Least-squares with gradient descent for a $66 \%$ - $33 \%$ split with 3 iterations for each $\alpha$.}
	\label{fig:reg_alphaRMSE}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.6in]{figures/lambdaRMSE.png}
	\caption{Ridge regression for a $66 \%$ - $33 \%$ split with 3 iterations for each $\lambda$.}
	\label{fig:reg_lambdaRMSE}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=3in]{figures/comparisonReg.png}
	\caption{Boxplots of train and test RMSE for least-squares (LS), least-squares with gradient descent (LS-GD) and ridge regression (Ridge) with $100$ iterations for each method.}
	\label{fig:reg_compareMethods}
\end{figure}

@@

\begin{figure}[!h] % !t
	\center
	\subfigure[Histogram of the $23^{th}$ dimension of $X$.]{\includegraphics[width=2.1in]{figures/dim23.png} \label{fig:class_dim23}}
	\hfill
	\subfigure[Histogram of the $35^{th}$ dimension of $X$.]{\includegraphics[width=2.1in]{figures/dim35.png} \label{fig:class_dim35}}
	\caption{Example of histogram to show the distribution of $X$ dimensions. We can see that each distribution is composed of a peak in blue and of a Gaussian in red, separable given the $20^{th}$ variable.}
\end{figure}

@@

Figure ~\ref{fig:class_penLogistic} shows the train and test loss function for $\lambda$ varied from $10^{-3}$ to $1$. We observe that changing $\lambda$ does not really improve the train and test loss function. The difference of error between train and test shows that the model is over-fitting. This is surely due to the amount of train data compared to the amount of test data, which is not high enough. However, we chose this split to make a cross-validation with similar train/test quantities to those we are provided to make output prediction.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.6in]{figures/lambdaLossBox.png}
	\caption{Penalised logistic regression for a $50 \% - 50\%$ split with 3 iterations for each $\lambda$.}
	\label{fig:class_penLogistic}
\end{figure}

@@

\subsubsection*{References}
Applied Machine Learning course notes from Aude Billard

PCML course notes from Mohammad Emtiyaz Khan
